\section{Glossary}
\begin{itemize}
	\item \textbf{Arranger team}\\
	All people part of Musik i Lejet but the members of the boards. This includes also teamleaders and one is used to reference to the total working force of the organisations. "Arrangør gruppen" in danish.
	\item \textbf{Team leader}\\
	The person whom after the recent restructuring of the organisation, is the main contact person of a group or space. While the title of team leader might insinuate a privileged position, this should rather be understood as a person in charge of keeping track of the progression in his own group in case a boardmember or other group is in need of the information.
	\item \textbf{Podio}\\
	Podio(\href{www.podio.com}{www.podio.com}) is a web based application and business platform to support organsization and communication internally in a team, company or organisation. As a member of an organisation on Podio, one has a profile of which one can discus, post content, create tasks or manage files for others colleagues can view, use and/or edit.
	\item \textbf{Podio workspace} \\
	Much like the platform facebooks \emph{groups}, Podio provides the option to divides members of an organisation into workspaces (aliased space), e.g. MiLs communication space.
	\item \textbf{Podio app}
	Podio as a platform consists of a collection of features such as a calenders, projects, and recruitment, which are defined (under the termonology of podio) as apps. Podio has a large library of predefined apps, and also offers the option to creating custom apps specified for the needs of the organisation. Each workspace has its own collection of apps.
	\item \textbf{Deadlines}\\
	In context of MiL the term deadline refers to the date of when a task should have been finalized. If a deadline has been met the task has been finalized and determined done before the date of the deadline.
	\item \textbf{Board}\\
	When refering to the board, one referes to the boardmembers of MiL. This is at the current time (December 2013): Tine Sorgenfrei, Søren Stakemann, samt Andreas og Kristian Grauengaard.
	\item \textbf{Management}\\
	The management consists of all teamleaders from the respective groups, being the representatives of the organs of MiL.
	\item \textbf{Arranger}\\
	An arranger is a contributer tosingle or multiple groups of MiL.
	\item \textbf{Hype}\\
	To promote or publicize extravagantly

\end{itemize}